Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-05-17 semantic-nd/article.tex
Rewritting of subsection 4.1: conditional probability.
It now explains why we use the factor graph produced by the conceptual layer.

In the presented case, the conditional probability is approximated by the graphical model $G$
produced by the conceptual layer.
\autoref{fig:conditional-prob-graph} presents a possible graph $G$ built from the conceptual
layer to represent the conditional probability on the sensed variables $x$.
$P_G(x)$ is used as an approximation for $P(x|\overline{novel})$.

\begin{figure}[h]
\centering
\includegraphics[width=0.70\textwidth]{figures/conditional-prob-graph.pdf}
\caption{\label{fig:conditional-prob-graph}The conceptual layer models the conditional
         probability distribution of the sensed variables by using hidden variables.
         Those are created from the conceptual knowledge and represent the structural
         and connectivity information the system is aware of.
         In this case only hidden variables $R_i$ were used to model the room categories
         where each property was sensed.}
\end{figure}

>>>>

The conditional probability models the distribution of variables given that the sample
is not novel for the agent.
This is: it should model the distribution of the sensed features considering that the
knowledge the agent possesses holds true. Under that its natural to model it with a graphical
model that combines the information acquired with the relations that the describe the
relations learned by the agent between the variables.

In Dora case, this is equivalent to use the graphical model used by it to describe its
current believes on the variables modelled by the system.
That graph is built, by the conceptual layer, by instancing the information extracted from
other layers together with the conceptual knowledge such as: objects are properties of rooms,
rooms are connected between each other.

\begin{figure}[h]
\centering
\includegraphics[width=0.70\textwidth]{figures/conditional-prob-graph.pdf}
\caption{\label{fig:conditional-prob-graph}A sample of a factor graph modelling a distribution
         of a set $x$ of sensed variables.}
\end{figure}

\autoref{fig:conditional-prob-graph} presents a possible graph $G$ built from the conceptual
layer to represent the conditional probability on the sensed variables $x$.
A set of hidden variables is added to represent the conceptual knowledge the system is aware of.
In the presented graph variables $R_i$ were added to model the room categories that influence
the directly sensed features on each physical room, as well connectivity factors between each
room.

The factors connecting the variables are trained by the system by searching databases of
common knowledge to build potentials describing how likely it is that a specific set of
values for a set of variables is more likely to occur over than any other set of values.
For instance: it is very likely to find a cereal box in a kitchen; and it is unlikely to find
bathroom connected to another bathroom.

We propose using such a graph $G$ built by the conceptual layer for modelling $P_G(x)$
as an approximation for $P(x|\overline{novel})$.
